Validation of an Actuator Line Model Coupled to a Dynamic Stall Model for Pitching Motions Characteristic to Vertical Axis Turbines

### 2016-08-21 paper.tex
Pithing --> pitching

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNRANSLES}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTRANSLES}}
\end{minipage}
\caption{\label{RANSLES}Normal (left) and tangential (right) force coefficients for different turbulence models, pithing motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNAMP174corrections}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTAMP174corrections}}
\end{minipage}
\caption{\label{AMP174corrections}Normal (left) and tangential (right) force coefficients with and without unsteady effects correction, pithing motion with a maximum amplitude of 17.4\degree\ }
\end{figure}

>>>>

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNRANSLES}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTRANSLES}}
\end{minipage}
\caption{\label{RANSLES}Normal (left) and tangential (right) force coefficients for different turbulence models, pitching motion with a maximum amplitude of 22.6\degree\ }
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CNAMP174corrections}}
%\resizebox{\columnwidth}{!}{\input{plot}}
\end{minipage}\hspace{2pc}%
\begin{minipage}{18pc}
\resizebox{\columnwidth}{!}{\input{./figures/CTAMP174corrections}}
\end{minipage}
\caption{\label{AMP174corrections}Normal (left) and tangential (right) force coefficients with and without unsteady effects correction, pitching motion with a maximum amplitude of 17.4\degree\ }
\end{figure}
